Australian Cancer Atlas

### 2020-01-14 Index.Rmd
rearrange site

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

@@

This is an animation that changes from a choropleth map to a hexagon tile map of Australian Statistical Areas at Level 2 using Standardised Incidence Ratios taken from the Australian Cancer Atlas website.

```{r}
knitr::include_graphics("melanoma_animation.gif")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width = "100%")
```

@@

```{r fig.cap = "This is an animation that changes from a choropleth map to a hexagon tile map of Australian Statistical Areas at Level 2 using Standardised Incidence Ratios taken from the Australian Cancer Atlas website."}
knitr::include_graphics("melanoma_animation.gif")
```

@@
